### 2015-07-08 2015-compmorphon-morphver/poster.tex
better flow chart?
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61221 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

\usepackage{fontspec}
\defaultfontfeatures{PunctuationSpace=2,Scale=MatchLowercase,Mapping=tex-text}
\newfontfeature{IPA}{+mgrk}
%\setromanfont[IPA]{FreeSerif}
%\setromanfont[IPA,Scale=0.8]{CMU Serif}
%\setromanfont[IPA]{Liberation Serif}
\setromanfont[IPA]{Linux Libertine O}
%\setromanfont[IPA]{Nimbus Roman No9 L}
\setmonofont[IPA]{DejaVu Sans Mono}
\usepackage[small,bf]{caption}
\newfontfamily\qipa[IPA,Scale=MatchLowercase]{FreeSerif}
\newfontfamily\qgmk[IPA,Scale=0.8]{CMU Serif}
\newfontfamily\litamono[IPA,Scale=0.5]{DejaVu Sans Mono}
\newfontfamily\ortamono[IPA,Scale=0.625]{DejaVu Sans Mono}

@@

	\headerbox{Further information}{name=getting,column=2,below=nedostatki}{
		\begin{itemize}
			\item Part of \textbf{Apertium Turkic} project:\\
			\url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
			\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
			\item \textbf{Source code} available from Apertium's svn repo
			%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Turkic RBMT \textbf{mailing list} (>25 subscribers):\\
			\texttt{apertium-turkic@lists.sourceforge.net}\\
			\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
			\item See our papers in LREC proceedings\\
			(2012:\ Kyrgyz, 2014:\ Kazakh, Tatar, Kumyk)
			\item And feel free to contact the authors any time!
		\end{itemize}
	}

@@

		\headerbox{References}{name=references,column=3,below=tuvanvowelharmony}{
			\begin{spacing}{0.85}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-1em}
		}

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			\begin{tikzpicture}[node distance = 2cm, auto]
				% Place nodes
				\node [block] (init) {analyse corpus};
				\node [cloud, left of=init] (addstem) {add stem};
				\node [cloud, right of=init] (fixphon) {fix phonology};
				\node [block, below of=init] (freq) {examine frequency list};
				%\node [block, below of=identify] (evaluate) {evaluate candidate models};
				%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
				\node [decision, below of=freq] (decide) {cause for unanalysed forms?};
				%\node [block, below of=decide, node distance=3cm] (stop) {stop};
				% Draw edges
				\path [line] (init) -- (freq);
				\path [line] (freq) -- (decide);
				\path [line] (decide) -| node [near start] {missing stem} (addstem);
				\path [line] (decide.east) -| node [near start] {bad phonology} (fixphon);
				\path [line,dashed] (addstem) -- (init);
				\path [line,dashed] (fixphon) -- (init);
			\end{tikzpicture}
		}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\newcommand{\flowchartscale}{0.65}
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{line} = [draw, -latex', thick, font=\diagsans]
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, text width=8em,
	text centered, %node distance=3cm,
	minimum height=2em, font=\diagsans, scale=\flowchartscale]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

\usepackage{fontspec}
\defaultfontfeatures{PunctuationSpace=2,Scale=MatchLowercase,Mapping=tex-text}
\newfontfeature{IPA}{+mgrk}
%\setromanfont[IPA]{FreeSerif}
%\setromanfont[IPA,Scale=0.8]{CMU Serif}
%\setromanfont[IPA]{Liberation Serif}
\setromanfont[IPA]{Linux Libertine O}
%\setromanfont[IPA]{Nimbus Roman No9 L}
\setmonofont[IPA]{DejaVu Sans Mono}
\usepackage[small,bf]{caption}
\newfontfamily\qipa[IPA,Scale=MatchLowercase]{FreeSerif}
\newfontfamily\qgmk[IPA,Scale=0.8]{CMU Serif}
\newfontfamily\litamono[IPA,Scale=0.5]{DejaVu Sans Mono}
\newfontfamily\ortamono[IPA,Scale=0.625]{DejaVu Sans Mono}
\newfontfamily\diagsans[IPA,Scale=1]{DejaVu Sans}

@@

	\headerbox{Further information}{name=getting,column=2,below=nedostatki}{
		\begin{itemize}
			\item Part of \textbf{Apertium Turkic} project:\\
			\url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
			\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
			\item \textbf{Source code} available from Apertium's SVN repo
			%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Turkic RBMT \textbf{mailing list} (>25 subscribers):\\
			\texttt{apertium-turkic@lists.sourceforge.net}\\
			\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
			\item And feel free to contact the authors any time!
		\end{itemize}
	}

@@

		\headerbox{References}{name=references,column=3,below=tuvanvowelharmony}{
			\begin{spacing}{0.7}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-0.5em}
		}

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			%\scalebox{0.8}{
			%\begin{tikzpicture}[node distance = 2cm, auto]
			%	% Place nodes
			%	\node [cloud, above of=fixphon] (assumed) at (5.5,1.5) {assumed phonology} ;
			%	\node [block] (init) at (1,3) {analyse corpus} ;
			%	\node [block, left of=init] (addstem) at (0,3) {add stem};
			%	\node [block, right of=init] (fixphon) at (3.5,3) {fix phonology};
			%	\node [block, below of=init] (freq) at (1,2) {examine frequency list};
			%	\node [decision, right of=freq] (break) at (1.5,0) {did something break?};
			%	%\node [block, below of=identify] (evaluate) {evaluate candidate models};
			%	%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
			%	\node [decision, below right of=freq] (decide) at (0,-1) {cause for unanalysed forms?};
			%	\node [cloud] (revised) at (6.75,-4.5) {revised phonology} ;
			%	%\node [block, below of=decide, node distance=3cm] (stop) {stop};
			%	% Draw edges
			%	\path [line] (init) -- (freq);
			%	\path [line] (freq) -- (break);
			%	\path [line] (break.south) -| node [near start] {no} (decide.north) ;
			%	\path [line] (break.north) -| node [near start] {yes}(fixphon.south) ;
			%	\path [line] (decide) -| node [near start] {missing stem} (addstem);
			%	\path [line] (decide.east) --(decide-|fixphon.east) node [below, midway] {bad phonology} |-(break.north-|fixphon.south) -- (fixphon.south);
			%	\path [line] (addstem) -- (init);
			%	\path [line] (fixphon) -- (init);
			%	\path [line,dashed] (assumed) -- (fixphon);
			%	\path [line,dashed] (fixphon.east) --(fixphon.east-|assumed.east) |-(decide.east-|revised.north) -- (revised.north);
			%\scalebox{0.65}{
			\begin{tikzpicture}[xscale=1.92,yscale=2.25]%, auto]

				\node[cloud] (assumptions) at (1,2.75) {assumed generalisations};
				\node[block] (analyse) at (1,2) {analyse corpus};
				\node[block] (check) at (1,1) {examine freq.\ list};
				\node[decision] (missingstem) at (1,0) {missing stem?};
				\node[block] (addstem) at (0,2) {add stem};
				\node[decision] (phonormorph) at (2,0) {type of problem?};
				\node[block] (updatephon) at (3,0) {update phonol.};
				\node[block] (updatemorph) at (3,1) {update morphol.};
				\node[decision] (phonbetter) at( 4,0) {better?};
				\node[decision] (morphbetter) at (4,1) {better?};
				\node[cloud] (newgeneralisation) at (2.5,2) {new\\grammatical\\generalisation};

				\path[line] (assumptions) -- (analyse);
				\path[line] (analyse) -- (check);
				\path[line] (check) -- node [right=0.75ex, scale=\flowchartscale, align=left] {unanalysed\\forms} (missingstem);
				\path[line] (missingstem) -| node [below=1ex, near start, scale=\flowchartscale] {yes} (addstem);
				\path[line] (addstem) -- (analyse);
				\path[line] (missingstem) -- node [below=1ex, midway, scale=\flowchartscale] {no} (phonormorph);
				\path[line] (phonormorph) -- node [below=1ex, near start, scale=\flowchartscale] {phon} (updatephon);
				\path[line] (phonormorph) |- node [below=1ex, near end, scale=\flowchartscale] {morph} (updatemorph);
				\path[line] (updatephon) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (phonbetter) ;
				\path[line] (updatemorph) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (morphbetter) ;
				\path[line] (phonbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.5,0) |- (newgeneralisation.east) ;
				\path[line] (morphbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.5,1) |- (newgeneralisation.east) ;
				\path[line] (phonbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,0.5) -| (updatephon.north) ;
				\path[line] (morphbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,1.5) -| (updatemorph.north) ;
				\path[line] (newgeneralisation) -- (analyse);

			\end{tikzpicture}%}
